---
title: C++ integration with Rcpp
author: ''
date: '2021-03-23'
slug: rcpp-integration
categories: []
tags: [Rcpp]
---


```{r warning=FALSE, include=FALSE}
library(Rcpp)
library(rbenchmark)
library(tidyverse)
```

# Benchmarking a computationally demanding function in R and C++

The Fibonacci sequence mathematically defined as $$F_n = \begin{cases}
n, & n\le 2\\
F_{n-1} + F_{n-2}, & n>2
\end{cases}$$


### R implementation

```{r}

f <- function(n){
  if (n < 2) return(n)
  return(f(n - 1)+f(n - 2))
}

sapply(1:10, f)

Rscores <- benchmark(f(10),f(15), f(20), f(25), f(30))[,1:4]

Rscores
```

```{r rplot}
p <- Rscores %>% 
  filter(elapsed>0) %>% 
  ggplot(aes(test,elapsed, group = 1))+
  geom_line()+theme_minimal()+
  labs(title = "Fibonacci function benchmarked in R",
       y = "time elapsed (seconds)",
       x = "Function and iteration") 
print(p)
```


### C++ implementation

The function defined above can be written within C++ as shown below and is callable from R through the Rcpp package. Rcpp::sourceCpp() is an option to source C++ files directly. Alternatively, the C++ function can be written within its own chunk using the Rcpp engine by using ```{Rcpp} as a code chunk header.

```{r}
# Rcpp::sourceCpp("g.cpp")
```

```{Rcpp}
#include <Rcpp.h>
//[[Rcpp::export]]
int g(int n) {
  if (n < 2) return(n);
  return(g(n-1) + g(n-2));
}
```


```{r}
sapply(0:10, g)



Cscores <- benchmark(g(10),g(15), g(20), g(25),g(30))[,1:4]

Cscores

```

```{r cplot}
p <- Cscores %>% 
  ggplot(aes(test,elapsed, group = 1))+
  geom_line()+ theme_minimal()+
  labs(title = "Fibonacci function benchmarked in C++",
       y = "time elapsed (seconds)",
       x = "Function and iteration")

print(p)
```

```{r include=FALSE}
last_elapsed_r <- Rscores %>% tail(1)

last_elapsed_r <- last_elapsed_r[[3]]

last_elapsed_c <- Cscores %>% tail(1)

last_elapsed_c <- last_elapsed_c[[3]]
```


# Conclusion
The speed in calculating the 30th iteration of the Fibonacci sequence within C++ (`r last_elapsed_c` seconds) massively outperforms R (`r last_elapsed_r` seconds).


## Pushing C++ further

```{r}


Cscores <- benchmark(g(10),g(15), g(20), g(25),g(30),g(35),g(40))[,1:4]

Cscores %>% 
  ggplot(aes(test,elapsed))+
  geom_point()+
  labs(title = "Pushing C++ further")+
  theme_minimal()
```
The function $f(35)$ takes around 15 minutes to complete in R. C++ can handle $g(40)$ in just 26 seconds. test3

