---
name: Ashleigh
surname: Sherlock
position: "BA Musical Theatre and Cabaret Performance"
address: "Benfleet, Essex"
phone: +44 7706 088840
email: "Ashsherlock98@outlook.com"
linkedin: AshleighSherlock?
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)



```

# Overview
 * Recent graduate in Musical Theatre and Cabaret Performance.
 * Special interest in R statistical programming, RShiny dashboards, data analysis and visualisation.
 * Seeking role within a finance & accounting, data analytics, or business analyst/intelligence function. 

# Education

```{r}

tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "BA in Musical Theatre and Cabaret Performance (Upper Second-Class with Honours)", "2023", "University of Chichester", "• Modules include: ",
  
  "A Levels: Performing Arts (A), Drama and Theatre Studies (A), English Lit (A), Fine Art (A)", "2017", "Sevic College", "",
  "GCSEs: 12 GCSEs A-C, including English, Maths, and Sciences", "2014", "The Appleton School", ""
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Employment

```{r}
tribble(
  
  ~ Degree, ~ Year, ~ Institution, ~ Where,
    "Production Vocalist and Entertainer/Host", "Jul 2023-Nov 2023", "Lyons Holiday Parks – Winkups and Oakfields","
  
  • Details about the role?
  ",
  
  "Vocalist (Main Stage)", "Jun 2023", "Chichester Pride","• Details about the role?
",

  "Patricia Bakewell", "Jun 2023", "Fat Club: A Comedy Musical –","• Details about the role?
 
",

  "Syd Lawrence Orchestra ‘Strictly Cabaret’", "May 2023", "The Kings Theatre
Portsmouth","• Details about the role
  
",

  "Marvelous Musicals", "Jan 2023", "Chichester Conservatoire","• Mama Morton /Anne of Cleves /Ensemble

",


  "A Christmas Carol the Concert UK Tour", "Jan 2023", "Great Immediately Productions","• Lead Soprano

",

  "Marvelous Musicals", "Jan 2023", "Chichester Conservatoire","• Mama Morton /Anne of Cleves /Ensemble

",

  "Marvelous Musicals", "Jan 2023", "Chichester Conservatoire","• Mama Morton /Anne of Cleves /Ensemble

",

  "Marvelous Musicals", "Jan 2023", "Chichester Conservatoire","• Mama Morton /Anne of Cleves /Ensemble

"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)

```

# Professional qualifications and awards

```{r}


tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Associate Member, Chartered Institute of Management Accountants", "", "CIMA", "",
  
    "CIMA Performance and Project Management","2023", "Association of International Certified Professional Accountants","Business Models and Leading and Managing People. Cert: https://RoyWilson.UK/tpm.pdf.",
  
     "2020 Digital Mindset AICPA certificate", "2020", "Association of International Certified Professional Accountants","Robotic Process Automation (RPA), blockchain technology, human intelligence, data analysis theory and the future of finance.",
  
   "CIMA Certificate in Business Accounting", "2018", "CIMA", "Fundamentals of Business Economics, Management Accounting, Financial Accounting, Ethics, Corporate Governance and Business Law.",
  
  "Vulnerable person safeguarding training.","2017", "Bangor University","",
 ) %>%
   detailed_entries(Degree, Year, Institution, Where)
```

<!-- [Verify 2020 Digital Mindset AICPA certificate](https://www.credly.com/badges/04ce8e24-971f-407b-94a0-c8b4c6f9756f/linked_in_profile) -->

\newpage

# Personal projects

```{r}
 tribble(
   ~ Degree, ~ Year, ~ Institution, ~ Where,
             "2021", "Dynamic documents", "Dynamic documents written in R markdown - including this CV!", "",
  "2021", "R markdown blogdown site", "Example of dynamically produced articles and a resource to keep track of useful code", "https://RoyWilson.UK",
  
    "2022", "R Shiny dashboard web application hosted on AWS", 'Publication: J.A. Wilson, L.J. Evitts, A. Fraile, R.E. Wilson, M.J.D. Rushton, D.T. Goddard, W.E. Lee, S.C. Middleburgh, "Predicting the Thermal Expansion of BCC High Entropy Alloys in the Mo-Nb-Ta-Ti-W System, (2022)", Journal of Physics: Energy. https://doi.org/10.1088/2515-7655/ac6f7e.', "https://Alloys.one",
            
  "2009-2013", "Visual Basic / VB.NET", "Experience building GUIs in a compiled language; experience in functional programming", "",
 ) %>% 
   detailed_entries(Year, Degree, Where, Institution)
```
# Professional skills

```{r}

 tribble(
   ~ Degree, ~ Year, ~ Institution, ~ Where,
  "2020", "R for Data Science", "Manipulating data, statistical modelling, functional programming, and advanced graphics in R.", "Jumping Rivers RSS Accredited",
  "2020", "PostgreSQL", "SQL fundamentals; familiarity with basic queries and aggregate functions.","Data Camp",
"", "Microsoft Office Suite", "Including Excel and Access, familiar with data functions (e.g. pivot tables) and working with relational databases.","",

"2019", "Programming Principles and Practice using Python", "Fundamental programming concepts and best practice.","Bangor Doctoral school",
"2019", "Advanced Python", "Exceptions; libraries; documentation and unit testing; mapping and fitlering; lambda functions; and additional tools.","Bangor Doctoral school",
"2019", "Introduction to the Linux Shell", "Navigating file structures; working with files and directories; standard out, standard error and pipes; loops; conditions; and re-use through scripts.","Bangor Doctoral school",
"", "Desire to expand on my knowledge of specialist tools for different applications","Interest in learning rapid development tools like Tableau, Alteryx, and Power BI.","",
"", "Full clean driver's licence","",""
 ) %>%
   detailed_entries(Year, Degree, Where, Institution)
```






# Hobbies and interests

```{r}
 tribble(
   ~ Degree, ~ Year, ~ Institution, ~ Where,
"","Welsh learner","
Learning to communicate through the medium of Welsh, attended the ysgol haf, and took part in the Ffrind Cymraeg project","",

"","Books and audiobooks","Avid consumer of audiobooks","",

"","Computing and data visualisation","Learning how to better represent data and honing my programming and computing skills","",

"2016-2018", "Treasurer at Bangor University Chess Society", "• Organised and delivered interactive sessions
  
  • Took control of purchases and delivered the society's budget", "Bangor University",

 ) %>%
   detailed_entries(Year, Degree, Where, Institution)
```

