---
name: Roy
surname: Wilson
position: "CIMA Dip MA, MSc, BSc"
address: "Bangor, Wales. Open to relocation"
phone: +44 777 617 5496
email: "Roy@RoyWilson.UK"
linkedin: RoyWilsonUK
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)



```

# Overview
 * Masters graduate in Accounting and Finance (Distinction). 
 * Special interest in R statistical programming, data analysis and visualisation.
 * Seeking role within a finance & accounting, data analytics, or business analyst/intelligence function. 

# Education

```{r}

tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "MSc in Accounting and Finance (Distinction)", "2019", "Bangor University & Fitch Learning", "• Modules include: Financial Analysis (78%), Management Accounting (83%), Accounting Theory (81%), 
  
  Financial Econometrics (65%), Research Methods (71%),
  
  
  Advanced Financial Reporting and Regulation (81%), International Financial Markets (64%). 
  
  • Summer project: Financial Research and CFA Series covering the CFA Level 1 syllabus and financial research titled 'the Role of Credit Rating Agencies' and 'Investigating the Efficient Market Hypothesis'.",
  "BSc in Accounting and Finance (First-Class with Honours)", "2018", "Bangor University", "Investment, Advanced Corporate Finance, Auditing, Advanced Investment Theory and Practice, 
  
  Corporate Risk Management, Financial Statement Analysis, Comparative Banking, Taxation, Advanced Accounting Theory and Practice, Statistical
Methods, Company Law for Business",
  "A Levels: Maths C, Accounts C, ICT C", "2015", "Birmingham Metropolitan College", "",
  "GCSEs: 8 GCSEs A-B, including English, Maths, and Sciences", "2013", "Beamont Collegiate Academy", ""
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Employment

```{r}
tribble(
  
  ~ Degree, ~ Year, ~ Institution, ~ Where,
    "Finance and payroll officer", "2021-Present", "Medical Resource Partners","
  
  • Payroll: ensuring candidates are paid correctly and clients are charged correctly each week. 
  
  • Credit control: reviewing invoices and ensuring a low volume of aged-debts.
  
  • Robotic Process Automation (RPA): automated processing of timesheets and routine processes.
  
  • Data analysis: with RShiny dashboards, and ad hoc insight into candidate and financial information.
  
  • Built a bespoke pay and bill solution integrating data with Xero and Paycircle payroll software. 
  
  • Automated production of sales and self-billing invoices written in RMarkdown and LaTeX.
  ",
  
  "Sales assistant", "2016-2022", "ASDA Stores Ltd.","• Provide excellent customer service
  
  • Perpetual inventory management, stock rotation, supported product recalls, routine processes
  
  • Setting up modular and promotional displays and merchandising
  
  • Familiar with maintaining KRAs and general store performance metrics
"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)

```

# Professional qualifications and awards

```{r}


tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Associate Member, Chartered Institute of Management Accountants", "", "CIMA", "",
   "CIMA Certificate in Business Accounting", "", "CIMA", "Fundamentals of Business Economics, Management Accounting, Financial Accounting, Ethics, Corporate Governance and Business Law",
   "2020 Digital Mindset AICPA certificate", "", "Association of International Certified Professional Accountants","Robotic Process Automation (RPA), blockchain technology, human intelligence, data analysis theory and the future of finance",
  "Vulnerable person safeguarding training","", "Bangor University","",
 ) %>%
   detailed_entries(Degree, Year, Institution, Where)
```

<!-- [Verify 2020 Digital Mindset AICPA certificate](https://www.credly.com/badges/04ce8e24-971f-407b-94a0-c8b4c6f9756f/linked_in_profile) -->

\newpage

# Personal projects

```{r}
 tribble(
   ~ Degree, ~ Year, ~ Institution, ~ Where,
             "2021", "Dynamic documents", "Dynamic documents written in R markdown - including this CV!", "",
  "2021", "R markdown blogdown site", "Example of dynamically produced articles and a resource to keep track of useful code", "https://RoyWilson.UK",
  
    "2022", "R Shiny dashboard web application", "Publication: J.A. Wilson, L.J. Evitts, A. Fraile, R.E. Wilson, M.J.D. Rushton, D.T. Goddard, W.E. Lee, S.C. Middleburgh, Predicting the thermal expansion of BCC high entropy alloys in the Mo-Nb-Ta-Ti-W system, (2022). https://doi.org/10.1088/2515-7655/ac6f7e.", "https://Alloys.one",
            
  "2009-2013", "Visual Basic / VB.NET", "Experience building GUIs in a compiled language; experience in functional programming", "",
 ) %>% 
   detailed_entries(Year, Degree, Where, Institution)
```
# Professional skills

```{r}

 tribble(
   ~ Degree, ~ Year, ~ Institution, ~ Where,
  "2020", "R for Data Science", "Manipulating data, statistical modelling, functional programming, and advanced graphics in R.", "Jumping Rivers RSS Accredited",
  "2020", "PostgreSQL", "SQL fundamentals; familiarity with basic queries and aggregate functions","Data Camp",
"", "Microsoft Office Suite", "Including Excel and Access, familiar with data functions (e.g. pivot tables) and working with relational databases","",

"2019", "Programming Principles and Practice using Python", "Fundamental programming concepts and best practice","Bangor Doctoral school",
"2019", "Advanced Python", "Exceptions; libraries; documentation and unit testing; mapping and fitlering; lambda functions; and additional tools","Bangor Doctoral school",
"2019", "Introduction to the Linux Shell", "Navigating file structures; working with files and directories; standard out, standard error and pipes; loops; conditions; and re-use through scripts","Bangor Doctoral school",
"", "Desire to expand on my knowledge of specialist tools for different applications","Interest in learning rapid development tools like Tableau, Alteryx, and Power BI.","",
"", "Full clean driver's licence","",""
 ) %>%
   detailed_entries(Year, Degree, Where, Institution)
```






# Hobbies and interests

```{r}
 tribble(
   ~ Degree, ~ Year, ~ Institution, ~ Where,
"","Welsh learner","
Learning to communicate through the medium of Welsh, attended the ysgol haf, and took part in the Ffrind Cymraeg project","",

"","Books and audiobooks","Avid consumer of audiobooks","",

"","Computing and data visualisation","Learning how to better represent data and honing my programming and computing skills","",

"2016-2018", "Treasurer at Bangor University Chess Society", "• Organised and delivered interactive sessions
  
  • Took control of purchases and delivered the society's budget", "Bangor University",

 ) %>%
   detailed_entries(Year, Degree, Where, Institution)
```

