---
name: Roy
surname: Wilson
position: "CIMA Cert BA, MSc, BSc"
address: "Bangor, Wales. Open to relocation."
phone: +44 777 617 5496
www: RoyWilson.UK
email: "Roy@RoyWilson.UK"
linkedin: RoyWilsonUK
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Overview
 * Masters graduate in Accounting and Finance (Distinction). 
 * Special interests in R statistical programming, data analysis and visualisation, and data processes automation.
 * Seeking role within a finance or data analytics function. 
 * 7 exam exemptions for the CIMA and ACCA qualifications. CIMA masters gateway route is available. 

# Education

```{r}

tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "MSc in Accounting and Finance (Distinction)", "2019", "Bangor University & Fitch Learning", "Financial Analysis (78%), Management Accounting (83%), Accounting Theory (81%), Financial Econometrics (65%), Research Methods (71%), Advanced Financial Reporting and Regulation (81%), International Financial Markets (64%). Summer project: Financial Research and CFA Series covering the CFA Level 1 syllabus with mock exam and 2 financial research assignments.",
  "BSc in Accounting and Finance (First-Class with Honours)", "2018", "Bangor University", "Investment, Advanced Corporate Finance, Auditing, Advanced Investment Theory and Practice, Corporate Risk Management, Financial Statement Analysis, Comparative Banking, Taxation, Advanced Accounting Theory and Practice, Statistical
Methods, Company Law for Business",
  "A Levels: Information Technology, C, Accounting, C, and Maths (stats), C", "2015", "Birmingham Metropolitan College", "",
  "GCSEs: 8 GCSEs A-B, including English, Maths, and Science", "2013", "Beamont Collegiate Academy", ""
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Employment

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "ASDA Stores Ltd.", "2016-Present", "","Sales assistant; experience giving great customer service; stock rotation; perpetual inventory management; training new colleagues; teamwork, leadership and delegation experience; supporting product recalls"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Professional qualifications and awards

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Vulnerable person safeguarding training","", "Bangor University","",
  "Associate Member, Chartered Institute of Management Accountants", "", "CIMA", "",
   "CIMA Certificate in Business Accounting", "", "CIMA", "Fundamentals of Business Economics, Management Accounting, Financial Accounting, Ethics, Corporate Governance and Business Law",
   "2020 Digital Mindset AICPA certificate", "", "CIMA","Robotic Process Automation (RPA), blockchain technology, human intelligence, data analysis theory and the future of finance"
  
 ) %>%
   detailed_entries(Degree, Year, Institution, Where)
```

[Verify 2020 Digital Mindset badge](https://www.credly.com/badges/04ce8e24-971f-407b-94a0-c8b4c6f9756f/linked_in_profile)

\newpage


# Projects

```{r}
 tribble(
   ~ Degree, ~ Year, ~ Institution, ~ Where,
             "2021", "Dynamic documents", "This CV was produced using code in R using the {vitae} package.", "",
  "2021", "Data analysis blog written in R markdown", "Example of dynamicly produced articles and a useful resource to keep track of useful code snippets", "RoyWilson.UK",
    "2020", "Dashboard web application written in R shiny", "Calculates the thermal expansion of High Entropy Alloys (HEAs) using the rule of mixtures approach - publication pending", "JackWilson.shinyapps.io/cterom/",
      "2016-2018", "Treasurer at Bangor University Chess Society", "Experience running interactive sessions; undertook a teaching role; managing purchases and the society's budget", "Bangor University",
        "2019", "Welsh language", "Pellach/further level", "Bangor University",
            "2009-2013", "Visual Basic / VB.NET", "Experience building GUIs in a compiled language; experience in functional programming", "",
 ) %>% 
   detailed_entries(Year, Degree, Where, Institution)
```


# Professional interests and skills

```{r}

 tribble(
   ~ Degree, ~ Year, ~ Institution, ~ Where,
  "2020", "R for Data Science", "Manipulating data, statistical modelling, functional programming, and advanced graphics in R. Familiar with the tiderverse and data.table packages", "Jumping Rivers RSS Accredited",
  "2020", "PostgreSQL", "SQL fundamentals; familiarity with basic queries and aggregate functions","Data Camp",
"", "Microsoft Office Suite", "Including Excel and Access, familiar with data functions (e.g. pivot tables) and working with relational databases","",
"", "Desire to expand on my knowledge of specialist tools for different applications", "","",
"2019", "Programming Principles and Practice using Python", "Fundamental programming concepts and best practice","Bangor Doctoral school",
"2019", "Advanced Python", "Exceptions; libraries; documentation and unit testing; mapping and fitlering; lanbda functions; additional tools","Bangor Doctoral school",
"2019", "Introduction to the Linux Shell", "Navigating file structures; working with files and directories; standard out, standard error and pipes; loops; conditions; re-use though scripts","Bangor Doctoral school"

 ) %>%
   detailed_entries(Year, Degree, Where, Institution)
```

## Professional and academic referees are available on request. 