---
title: Metallurgical data
author: ~
date: '2020-07-03'
slug: compositional-analysis
categories: []
tags: []
---


```{r setup, include=FALSE, message=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = T,warning = FALSE, message = FALSE)
```

```{r message=FALSE, warning=FALSE, include=FALSE}

#library(robustbase)
#library(energy)
#library(gtools)
library(compositions)
library(readr)
library(tidyverse)
library(neuralnet)
library(caret)
library(caretEnsemble)
library(httr)
library(readxl)
```

```{r}
divide01 <- function(x){
  return(x/100)
}

data <- read.csv("hardness.csv") %>% 
  mutate(Al=divide01(Al),
         Co=divide01(Co),
         Cr=divide01(Cr),
         Cu=divide01(Cu),
         Fe=divide01(Fe),
         Ni=divide01(Ni))
data_ordered <- read.csv("hardness.csv") %>% 
  mutate(Al=divide01(Al),
         Co=divide01(Co),
         Cr=divide01(Cr),
         Cu=divide01(Cu),
         Fe=divide01(Fe),
         Ni=divide01(Ni)) %>% 
  arrange(desc(hardness))

closed <- clo(data, parts = 1:6,total=100)
cx <- acomp(data, c("Al","Co","Cr"))
plot(cx)
xc <- acomp(data, c("Al","Co","Cr","Cu","Fe","Ni"))
xc_ordered <- acomp(data_ordered, c("Al","Co","Cr","Cu","Fe","Ni"))
plot(xc)
barplot.acomp(xc)

```

Order of hardness desc



```{r}

barplot.acomp(xc_ordered)
         
```

Possibly drop copper and nickel


```{r}
library(httr)
raw_dd <- read.table(text=content(GET("https://gist.githubusercontent.com/MrFlick/c1183c911bc5398105d4/raw/715868fba2d0d17a61a8081de17c468bbc525ab1/elements.txt")), sep=",", header=TRUE) %>%
  mutate(ElementName=ifelse(ElementName=="Sulfer","Sulfur",ElementName),
         ElementName=ifelse(ElementName=="Phosphorous","Phosphorus",ElementName),
         ElementName=ifelse(ElementName=="Flourine","Fluorine",ElementName))
data <- read_xlsx("melting_points.xlsx", sheet = 'Sheet2')
colnames(raw_dd) <- c(colnames(raw_dd)[1:7],"element",colnames(raw_dd)[9:13])

 

dd <- raw_dd %>%
  left_join(data, by = "element") %>%
  mutate(CTE_ppm=CTE*1000000,
         CTE_ppm=as.numeric(CTE_ppm),
         scaled_cte=CTE_ppm,
         scaled_cte=ifelse(scaled_cte>8,8,scaled_cte),
         scaled_cte=ifelse(scaled_cte<4.5,4.4,scaled_cte),
         new_structure=ifelse(crystal_structure %in% c("Body-centered Cubic","Face-centered Cubic","Simple Hexagonal"),crystal_structure,NA))

 

 

dd %>%
  ggplot(aes(Column,-Row)) +
  geom_tile(aes(fill=crystal_structure), color="black") +
  geom_text(aes(Column, -Row,label= symbol))+
  theme_void()+
  labs(
    fill = "Crystal Structure"
  ) +
  annotate("text", x = 7, y = 0.2, label = "Periodic Table of the elements", size = 5)

 

dd %>%
  count(crystal_structure)

 

(p<-dd %>%
  filter(!is.na(symbol)) %>%
  #filter(!crystal_structure %in% c("Base-centered Monoclinic","Centered Tetragonal")) %>%
  ggplot(aes(Column, -Row))+
  geom_tile(aes(fill=scaled_cte), color="black",size=1) +
  geom_rect(aes(xmin=Column-0.3,xmax=Column+0.3,ymin=-Row-0.2,ymax=-Row+0.3,colour=new_structure),size=1,lty=1,fill="black")+
    #geom_text(aes(label="",colour=new_structure), na.rm = T,size=12,nudge_y = 0.3)+
  geom_text(aes(label=symbol),colour="yellow",nudge_y = +0.05)+
  geom_text(aes(label=CTE_ppm),colour="black",nudge_y = -0.35)+
  scale_fill_gradient(low = "red",high = "green")+
  labs(fill = expression(paste("CTE", 10^6)),
    colour="") +
  annotate("text", x = 7, y = 0.2, label = "Periodic Table of the elements", size = 5))+
  theme_void()+
  theme(legend.position="bottom")+
  scale_colour_discrete(na.translate = F)


```



```{r}

f1 <- function(x){
  return(1/(16.6*3*(x+273)))
}


library(plotly)
library(ggrepel)
data %>% 
  ggplot(aes(mp, CTE, label=element))+
  geom_point()+
  stat_function(fun=f1)+
  lims(
    x=c(1500,4000),
    y=c(0,0.000025)
  )+
  theme(legend.position = "none")+
  ggrepel::geom_text_repel()+
  theme_classic()


```
### Predictive modelling

Compositional data can be transformed to satisfy linearity by using logratio transformations. Additive, isometric, and centre logratio transformations are available. 

These transformation functions are available within the 'compositions' R package. Ratio transformations have issues with zero-value elements.

PRINCIPLES OF COMPOSITIONAL DATA ANALYSIS
BY JOHN AITCHISON


```{r}
library(compositions)
library(caret)
library(glmnet)
hard <- read_csv("hardness.csv")
#hard %>% arrange(-hardness)
```


```{r}
#v <- tibble(data.frame(Al = c(16.6666,40), Co = c(16.6666,20), Cr = c(16.6666,19), Cu = c(16.6666,1), Fe = c(16.66667,19), Ni =c(16.6666,1), hardness = 0))
#v
# Filtering out zero values for logratio transformations
hard_ <- hard %>% 
  filter(Al > 0, Co > 0, Cr > 0, Cu > 0, Fe > 0, Ni > 0)

# Setting x, y
y <- hard_$hardness
x <- hard_[,1:ncol(hard)-1]




hard.clr <- x %>% 
  clr()
hard.ilr <- x %>% 
  ilr()
hard.alr <- x %>% 
  alr()

#predict(hard.clr.lm,clr(v))

hard.clr.lm <- lm(y ~ ., cbind(y,hard.clr) %>% data.frame())
hard.ilr.lm <- lm(y ~ ., cbind(y,hard.ilr) %>% data.frame())
hard.alr.lm <- lm(y ~ ., cbind(y,hard.alr) %>% data.frame())

hard.ilr.glm.model <- cv.glmnet(hard.ilr, y, alpha = 1)
hard.ilr.glm <- glmnet(hard.ilr, y, alpha = 1, lambda = hard.ilr.glm.model$lambda.min)

library(mgcv)
dataset <- cbind(data.frame(hardness = y),hard.clr) %>% data.frame()
dataset
hard.clr.gam <- gam(hardness ~ Al+ Co + Co + Cr + Cu + Fe + Ni, data = dataset)




#hard_ <- rbind(v, hard_)


predictions.full <- data.frame(hard_) %>% 
  mutate(prediction.clr.lm = predict(hard.clr.lm, newx = hard_),
         prediction.ilr.lm = predict(hard.ilr.lm, newx = hard.ilr),
         #prediction.alr.lm = predict(hard.alr.lm, newx = hard.alr),
         prediction.ilr.glm = predict(hard.ilr.glm, best_lambda = hard.ilr.glm.model$lambda.min, newx = hard.ilr),
         prediction.clr.gam = predict(hard.clr.gam, newx = hard.clr),
         pre = predict(hard.clr.lm, newx = row()))



```


```{r}
predictions.full %>% colnames

predictions.full %>% 
  arrange(hardness) %>% 
  mutate(row_name = row_number()) %>% 
  pivot_longer(c(hardness, prediction.clr.lm,prediction.ilr.glm, prediction.clr.gam), names_to = "variable",values_to = "value") %>% #prediction.alr.lm
  ggplot(aes(row_name, value, colour = variable), size = 3)+
  geom_line(size = 2)+
  labs(title = "Hardness prediction",
       subtitle = "Comparing hardness prediction.alr.lm and actual hardness",
       y = "hardness",
       x = "rank ordered by ascending hardness")+
  annotate("text", y = 200, x = 25,label = paste("RMSE = ",
    round(RMSE(predictions.full$prediction.clr.lm, predictions.full$hardness),2)
  ))+
  theme_bw() 
```


```{r}

 

# Linear regression on ILR logratio transformation  
RMSE(predictions.full$prediction.clr.lm, predictions.full$hardness)

# Lasso regression on ILR logratio transformation
RMSE(predictions.full$prediction.ilr.glm, predictions.full$hardness)

# generalised additive model
RMSE(predictions.full$prediction.clr.gam, predictions.full$hardness)



```

```{r}
predictions.full %>% 
  arrange(desc(prediction.clr.gam))
```

```{r}
library(MASS)

y

x

library(Compositional)

y
mod1 <- comp.reg(y, cbind(y,x))
?comp.reg

mod2 <- comp.reg(y, x, type = "spatial")
```



