---
title: Election2019
author: Roy
date: '2020-07-01'
slug: bbc-style-ggplot
categories: []
tags: []
---

```{r setup, include=TRUE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(readr)
library(plotly)
library(bbplot)
theme_set(theme_bw())
addtimes <- function(date,roy,jack){

}

time_to_seconds <- function(x){
100*(x-floor(x))+floor(x)*60  
}

data_raw <- read.csv('data.csv')

data <- data_raw %>% 
  select(date,roy_time,jack_time) %>% 
  mutate(roy_time = roy_time / 60,
         jack_time = jack_time / 60) %>% 
  pivot_longer(c(roy_time,jack_time), names_to="person",values_to = "time")


```

```{r echo=FALSE, include = FALSE}
p <- data %>% 
  ggplot(aes(date,time,colour=person, group = person))+
  geom_line(size=2)+
  scale_color_discrete(name='Rebel',labels=c('Jack','Roy'))+
  labs(
    title='Jack & Roy running times 1.6 mile',
    x="",
    y="Time in minutes"
  )+
  scale_y_continuous(labels=scales::label_number_auto())

ggplotly(p)
```


```{r message=FALSE, include=TRUE}
library(tidyverse)
#setwd("~/University/R/election2019")
library(readr)
election <- read_csv("HoC-2019GE-results-by-constituency.csv") %>% 
  mutate(con_p=con/valid_votes,
         lab_p=lab/valid_votes,
         brexit_p=brexit/valid_votes,
         ld_p=ld/valid_votes,
         snp_p=snp/valid_votes)
```

### Voting mix of the most populated constituencies

```{r, message=FALSE, warning=FALSE}
party_colours <- c("purple", "dodgerblue", "red","orange","yellow")
election %>% 
  arrange(desc(valid_votes)) %>% 
  mutate(constituency_name=fct_reorder(constituency_name,con_p)) %>% 
  head(30) %>% 
  gather(key="Party", value="Number", con, lab, ld, snp, brexit) %>% 
  ggplot(aes(constituency_name,Number,fill=Party))+
  geom_col()+
  scale_fill_manual(values=party_colours)+
  coord_flip()+
  bbc_style()
```

### Voting mix of the least populated constituencies


```{r, message=FALSE, warning=FALSE}
election %>% 
  arrange(valid_votes) %>% 
  mutate(constituency_name=fct_reorder(constituency_name,valid_votes)) %>% 
  head(30) %>% 
  gather(key="Party", value="Number", con, lab, ld, snp, brexit) %>% 
  ggplot(aes(constituency_name,Number,fill=Party))+
  geom_col()+
  scale_fill_manual(values=party_colours)+
  coord_flip()+
  bbc_style()
```

### Where are the Conservative strongholds?

```{r, message=FALSE, warning=FALSE}
election %>% 
  arrange(desc(con_p)) %>% 
  mutate(constituency_name=fct_reorder(constituency_name,con_p)) %>% 
  head(30) %>%
  gather(Party, Proportion, con_p, lab_p, ld_p, brexit_p, snp_p) %>% 
  ggplot(aes(constituency_name,Proportion, fill = Party))+
  geom_col()+
  scale_fill_manual(values=party_colours)+
  scale_y_continuous(label=scales::percent_format()) +
  coord_flip()+
  bbc_style()
```


### Brexit Party significance

```{r, message=FALSE, warning=FALSE}

election %>% 
  view()
election %>% 
  mutate(constituency_name=fct_reorder(constituency_name, -con_p)) %>% 
  arrange(con_p) %>% 
  gather(Party, Proportion, con_p, lab_p, snp_p, brexit_p, ld_p) %>% 
  ggplot(aes(constituency_name, Proportion, fill = Party)) +
  geom_col()+
  scale_fill_manual(values=party_colours)+
  scale_x_discrete(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  labs(
    x="",
    y="Vote Share"
  )+
 bbc_style()+
  theme(axis.text.x = element_blank())
```



```{r, message=FALSE, warning=FALSE}
election %>% 
  ggplot(aes(con_p)) +
  geom_histogram(fill=party_colours[2])+
  bbc_style()
election %>% 
  ggplot(aes(lab_p))+
  geom_histogram(fill=party_colours[3])+
  bbc_style()
election %>% 
  ggplot(aes(brexit_p))+
  geom_histogram(fill=party_colours[1])+
  bbc_style()
election %>%
  filter(!brexit_p==0) %>% 
  ggplot(aes(brexit_p))+
  geom_histogram(fill=party_colours[1])+
  bbc_style()
```

```{r, message=FALSE, warning=FALSE}
election_noscotland <- election %>% 
  filter(!country_name=="Scotland")
  
model.lm <- lm(brexit_p ~ con_p + lab_p + ld_p, data = election_noscotland)
library(broom)
tidy(model.lm)
```
```{r, message=FALSE, warning=FALSE}
election_wales <- election %>% 
  filter(country_name=="Wales")
model.lm <- lm(brexit_p ~ con_p + lab_p + ld_p, data = election_wales)
tidy(model.lm)

```

Significant evidence shows that the participation of the Brexit Party in the election tends to reduce the Conservative vote share. Conversely, as the Brexit Party vote share increases, the Labour vote share increases by a small amount. This may suggest that the selective nature of the Brexit Party choosing which seats to contest has aided the Conservatives in the FPTP system. 

