---
title: Time-series and yfinance api
author: ~
date: '2020-07-07'
slug: time-series-and-yfinance-api
categories: []
tags: []
---

Python integration using the reticulate package.

yFinance api from https://pypi.org/project/yfinance/


```{r setup, include=FALSE, message=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = F,warning = FALSE, message = FALSE)
```


```{r}
library(reticulate)
library(tidyverse)
library(bbplot)
library(lubridate)
library(broom)
library(plotly)
library(readxl)

use_miniconda()
```



```{python}
import yfinance as yf
import requests

def yfinance01(ticker,period):
    g = yf.Ticker(ticker)
    data=g.history(period=period)
    return data
    
```


```{r}

fixcol01 <- function(g){
  g <- cbind(date = rownames(g), g)
  rownames(g) <- 1:nrow(g)
  return(g)
}

retrieve01 <- function(ticker,period="max"){
  g <- py$yfinance01(ticker,period)
  g <- fixcol01(g)
  g <- g %>% 
    select(date, Close)%>% 
    mutate(date=as_date(ymd(date)))
  colnames(g) <- c("date", ticker)
  return(g)
}

plotting01 <- function(ticker, period="max"){
  g <- retrieve01(ticker, period)
  plot <- g %>%  
    ggplot(aes(date, get(ticker), group=1))+
    geom_point(shape=".")+
    labs(title=ticker)+
    theme_void()+
    scale_y_continuous()+
    theme(axis.text = element_text())+
    geom_line(size=1)
  return(plot)
}

multiplot <- function(...,
                      period = "max",
                      length = 1000) {
  x <- list(...)
  y <-
    data.frame("date" = c(seq(
      today() - length, by = "day", length.out = length
    )))
  for (val in x) {
    #y <- left_join(y, retrieve01(val, period),by=c("date"))
    y <-
      merge(y,
            retrieve01(val, period),
            by = "date",
            allow.cartesian = TRUE)
  }
  h <- y %>%
    pivot_longer(cols = c(...),
                 names_to = "ticker",
                 values_to = "price")
  return(h)
}

decomp <- function(x) {
  data <- read_excel(x, sheet = 3,col_names = T)
  namesheet <- read_excel(x, sheet = 1,col_names = FALSE)
  data.frame(
    "id" = c(1:5),
    "ROCE" = c(
      paste(as.numeric(data[7, 3])),
      paste(as.numeric(data[7, 4])),
      paste(as.numeric(data[7, 5])),
      paste(as.numeric(data[7, 6])),
      paste(as.numeric(data[7, 7]))
    ),
    "year" = c(
      paste(data[4, 3]),
      paste(data[4, 4]),
      paste(data[4, 5]),
      paste(data[4, 6]),
      paste(data[4, 7])
    ),
    company = paste(namesheet[1, 1]),
    "RNOA" = c(
      paste(as.numeric(data[9, 3])),
      paste(as.numeric(data[9, 4])),
      paste(as.numeric(data[9, 5])),
      paste(as.numeric(data[9, 6])),
      paste(as.numeric(data[9, 7]))
    ),
    "FLEV" = c(
      paste(as.numeric(data[10, 3])),
      paste(as.numeric(data[10, 4])),
      paste(as.numeric(data[10, 5])),
      paste(as.numeric(data[10, 6])),
      paste(as.numeric(data[10, 7]))
    ),
    "NBC" = c(
      paste(as.numeric(data[11, 3])),
      paste(as.numeric(data[11, 4])),
      paste(as.numeric(data[11, 5])),
      paste(as.numeric(data[11, 6])),
      paste(as.numeric(data[11, 7]))
    ),
    "spread" = c(
      paste(as.numeric(data[12, 3])),
      paste(as.numeric(data[12, 4])),
      paste(as.numeric(data[12, 5])),
      paste(as.numeric(data[12, 6])),
      paste(as.numeric(data[12, 7]))
    ),
    "PM" = c(
      paste(as.numeric(data[15, 3])),
      paste(as.numeric(data[15, 4])),
      paste(as.numeric(data[15, 5])),
      paste(as.numeric(data[15, 6])),
      paste(as.numeric(data[15, 7]))
    ),
    "ATO" = c(
      paste(as.numeric(data[16, 3])),
      paste(as.numeric(data[16, 4])),
      paste(as.numeric(data[16, 5])),
      paste(as.numeric(data[16, 6])),
      paste(as.numeric(data[16, 7]))
    ),
    "GPM" = c(
      paste(as.numeric(data[20, 3])),
      paste(as.numeric(data[20, 4])),
      paste(as.numeric(data[20, 5])),
      paste(as.numeric(data[20, 6])),
      paste(as.numeric(data[20, 7]))
    ),
    "operating expense over sales" = c(
      paste(as.numeric(data[21, 3])),
      paste(as.numeric(data[21, 4])),
      paste(as.numeric(data[21, 5])),
      paste(as.numeric(data[21, 6])),
      paste(as.numeric(data[21, 7]))
    ),
    "taxes_over_sales" = c(
      paste(as.numeric(data[22, 3])),
      paste(as.numeric(data[22, 4])),
      paste(as.numeric(data[22, 5])),
      paste(as.numeric(data[22, 6])),
      paste(as.numeric(data[22, 7]))
    ),
    "other_income_over_sales" = c(
      paste(as.numeric(data[23, 3])),
      paste(as.numeric(data[23, 4])),
      paste(as.numeric(data[23, 5])),
      paste(as.numeric(data[23, 6])),
      paste(as.numeric(data[23, 7]))
    ),
    "one_over_ATO" = c(
      paste(as.numeric(data[26, 3])),
      paste(as.numeric(data[26, 4])),
      paste(as.numeric(data[26, 5])),
      paste(as.numeric(data[26, 6])),
      paste(as.numeric(data[26, 7]))
    ),
    "cash over sales" = c(
      paste(as.numeric(data[27, 3])),
      paste(as.numeric(data[27, 4])),
      paste(as.numeric(data[27, 5])),
      paste(as.numeric(data[27, 6])),
      paste(as.numeric(data[27, 7]))
    ),
    "receivables over sales" = c(
      paste(as.numeric(data[28, 3])),
      paste(as.numeric(data[28, 4])),
      paste(as.numeric(data[28, 5])),
      paste(as.numeric(data[28, 6])),
      paste(as.numeric(data[28, 7]))
    ),
    "inventory_over_sales" = c(
      paste(as.numeric(data[29, 3])),
      paste(as.numeric(data[29, 4])),
      paste(as.numeric(data[29, 5])),
      paste(as.numeric(data[29, 6])),
      paste(as.numeric(data[29, 7]))
    ),
    "other_current_assets_over_sales" = c(
      paste(as.numeric(data[30, 3])),
      paste(as.numeric(data[30, 4])),
      paste(as.numeric(data[30, 5])),
      paste(as.numeric(data[30, 6])),
      paste(as.numeric(data[30, 7]))
    ),
    "PPE_over_sales" = c(
      paste(as.numeric(data[31, 3])),
      paste(as.numeric(data[31, 4])),
      paste(as.numeric(data[31, 5])),
      paste(as.numeric(data[31, 6])),
      paste(as.numeric(data[31, 7]))
    ),
    "accounts_payable_over_sales" = c(
      paste(as.numeric(data[33, 3])),
      paste(as.numeric(data[33, 4])),
      paste(as.numeric(data[33, 5])),
      paste(as.numeric(data[33, 6])),
      paste(as.numeric(data[33, 7]))
    ),
    "income_taxes_over_sales" = c(
      paste(as.numeric(data[34, 3])),
      paste(as.numeric(data[34, 4])),
      paste(as.numeric(data[34, 5])),
      paste(as.numeric(data[34, 6])),
      paste(as.numeric(data[34, 7]))
    ),
    "other_liabilities_over_sales" = c(
      paste(as.numeric(data[35, 3])),
      paste(as.numeric(data[35, 4])),
      paste(as.numeric(data[35, 5])),
      paste(as.numeric(data[35, 6])),
      paste(as.numeric(data[35, 7]))
    )
  )
}

extract_eps <- function(x,name) {
  data <- read_excel(x, sheet = 1,col_names = F)
  namesheet <- read_excel(x, sheet = 1,col_names = FALSE)
  return(data.frame(
    "id" = c(2019:2015),
    "net_earnings" = c(
      paste(as.numeric(data[43, 3])),
      paste(as.numeric(data[43, 4])),
      paste(as.numeric(data[43, 5])),
      paste(as.numeric(data[43, 6])),
      paste(as.numeric(data[43, 7]))
    ),
    "name" = c(
      paste(name),
      paste(name),
      paste(name),
      paste(name),
      paste(name)
    )
    ))
}
```





```{r}
tsla <- multiplot("TSLA","HYMTF", "FCAU","RACE","NSANY","F","BMW.MI","BMW.DE","HMC","GM","VOW.DE","TM", period = "max",length = 30) %>% 
  filter(!is.na(price),
         price>1) %>%
  group_by(ticker) %>% 
  mutate(percentage_price = ((price/lag(price,1)) - 1)) %>%
  ungroup() %>% 
  mutate(market_state=case_when(percentage_price>0.02 ~ "+",
                                 percentage_price<(-0.02)~ "-",
                                 TRUE ~ ""))
tsla_states <- tsla %>%
  filter(ticker=="TSLA")

tsla %>% 
  mutate(is_tesla=ifelse(ticker=="TSLA",1,0)) %>% 
   ggplot()+
   geom_rect(data=tsla_states,aes(fill=market_state,xmin=date,ymin=ifelse(market_state=="+",0,percentage_price),xmax=date+1,ymax=ifelse(market_state=="+",percentage_price,0)),alpha=0.3)+
  scale_color_manual(values = c("white","red", "green"),aesthetics = c("fill"))+
  geom_step(aes(date, percentage_price, colour = ticker, alpha=ifelse(is_tesla==1,1,0.5)))+
   theme_void()+
  labs(colour = "Ticker",
       title="")+
  geom_line(stat="smooth",aes(date,percentage_price,group=is_tesla,alpha=ifelse(is_tesla==1,1,0.6)),colour="blue",lty=3,size=1,se=F,method="lm")+
  geom_vline(xintercept = today()-1,lty=2)+
  geom_hline(yintercept = 0)+
  annotate("text",label="Tesla (TSLA) monthly price change",x=today()-20,y=-0.15)+
  annotate("text",label=today(),colour="black",x=today()-2,y=-0.1,angle=90)+
  labs(title="Tesla (TSLA)",
       subtitle="Tesla and top global car producers % price change")+
  annotate("text",label=paste("+",round((tsla_states$price[length(tsla_states$price)]-tsla_states$price[1])/tsla_states$price[1]*100,2),"%",sep=""),colour="black",x=today()-20,y=-0.1,size=20)+
  scale_y_continuous(labels=scales::percent_format())+
  theme(axis.text = element_text(),
        legend.position = "none")+
  lims(x=c(today()-28,today()))



```


```{r}
share_prices <- multiplot("TSLA","HYMTF", "FCAU","RACE","NSANY","F","BMW.MI","BMW.DE","HMC","GM","VOW.DE","TM", period = "max",length = 1825) %>% 
  filter(!is.na(price),
         price>1) %>%
  mutate(price=price)

 
 share_prices %>% 
  ggplot()+
  geom_line(aes(date, price, colour = ticker))+
  geom_smooth(aes(date, price, colour = ticker),se = F)+
   scale_y_log10(labels=scales::dollar_format())+
  theme_void()+
  labs(colour = "Ticker",
       title="Share prices of global car companies (5year)")+
  theme(axis.text = element_text(),
        legend.position = "bottom")

```


### <i>"Global stocks have worst day in two years as coronavirus fears spread"</i> - FT 24th Feb 2020

https://www.ft.com/content/5ec9aeae-56a1-11ea-a528-dd0f971febbc


```{r}
data <- multiplot("TSLA","HYMTF", "FCAU","RACE","NSANY","F","BMW.MI","BMW.DE","HMC","GM","VOW.DE","TM", period = "max",length = 400) %>% 
  filter(!is.na(price),
         price>1) %>%
  group_by(ticker) %>% 
  mutate(percentage_price = ((price/lag(price,7)) - 1)) %>%
  ungroup() %>% 
  group_by(date) %>% 
   mutate(market_state=case_when(percentage_price>0 ~ "+",
                                 percentage_price<(-0)~ "-",
                                 TRUE ~ "")) 


data %>% 
   ggplot()+
   geom_rect(aes(fill=market_state,xmin=date-5,xmax=date+5,ymin=ifelse(market_state=="+",0,percentage_price),ymax=ifelse(market_state=="+",percentage_price,0)),alpha=0.03)+
  scale_color_manual(values = c("white","red", "green"),aesthetics = c("fill"))+
  geom_step(aes(date, percentage_price, colour = ticker))+
  geom_hline(yintercept = 0)+
  ggdark::dark_theme_minimal()+
  scale_y_continuous(labels=scales::percent_format())+
  labs(colour = "Ticker",
       title="Industry share prices changes of global car companies (1year)",
  y="",x="")+
    annotate("text",label="Covid-19",colour="white",x=ymd("20200216"),y=-0.4,angle=90)+
    geom_vline(xintercept = ymd("20200224"),lty=2,colour="grey")+
  theme(axis.text = element_text(),
        legend.position = "none")+
  lims(x=c(today()-365,today()))

 



```


```{r}
tsla <- multiplot("TSLA","HYMTF", "FCAU","RACE","NSANY","F","BMW.MI","BMW.DE","HMC","GM","VOW.DE","TM", period = "max",length = 400) %>% 
  filter(!is.na(price),
         price>1) %>%
  group_by(ticker) %>% 
  mutate(percentage_price = ((price/lag(price,7)) - 1)) %>%
  ungroup() %>% 
  mutate(market_state=case_when(percentage_price>0.00 ~ "+",
                                 percentage_price<(-0.00)~ "-",
                                 TRUE ~ ""))
tsla_states <- tsla %>%
  filter(ticker=="TSLA")

tsla %>% 
   ggplot()+
   geom_rect(data=tsla_states,aes(fill=market_state,xmin=date-5,ymin=ifelse(market_state=="+",0,percentage_price),xmax=date+5,ymax=ifelse(market_state=="+",percentage_price,0)),alpha=0.05)+
  scale_color_manual(values = c("white","red", "green"),aesthetics = c("fill"))+
  geom_step(aes(date, percentage_price, colour = ticker))+
  ggdark::dark_theme_minimal()+
  geom_hline(yintercept = 0)+
  scale_y_continuous(labels=scales::percent_format())+
  labs(colour = "Ticker",
       title="Tesla share prices changes (1year)")+
  annotate("text",label="Covid-19",colour="white",x=ymd(20200216),y=-0.4,angle=90)+
  geom_vline(xintercept = ymd("20200224"),lty=2)+
  labs(y="",
       x="")+
  theme(axis.text = element_text(),
        legend.position = "none")+
  lims(x=c(today()-365,today()))


```



# Car industry financial analysis 
A profitability decomposition analysis with a focus on Tesla (TSLA)

```{r echo=F, include=F}



eps <- extract_eps("Decompositions\\Raw income statements\\Ferrari.xls", name="Ferrari") %>% 
  union_all(extract_eps("Decompositions\\Raw income statements\\Fiat Chrysler.xls", name="Ferrari")) %>% 
  union_all(extract_eps("Decompositions\\Raw income statements\\Ford.xls", name="Ford")) %>% 
  union_all(extract_eps("Decompositions\\Raw income statements\\GM.xls", name="GM")) %>% 
  union_all(extract_eps("Decompositions\\Raw income statements\\Honda.xls", name="Honda")) %>% 
  union_all(extract_eps("Decompositions\\Raw income statements\\Hyundai.xls", name="Hyundai")) %>% 
  union_all(extract_eps("Decompositions\\Raw income statements\\Nissan.xls", name="Nissan")) %>% 
  union_all(extract_eps("Decompositions\\Raw income statements\\Tesla.xls", name="Tesla")) %>% 
  union_all(extract_eps("Decompositions\\Raw income statements\\Toyota.xls", name="Toyota")) %>% 
  union_all(extract_eps("Decompositions\\Raw income statements\\Volkswagen.xls", name="Ferrari")) %>% 
  union_all(extract_eps("Decompositions\\Raw income statements\\BMW.xls", name="BMW")) %>% 
  union_all(extract_eps("Decompositions\\Raw income statements\\Daimler.xls", name="Daimler"))




```



```{r message=F, warning= F}

profitability <- decomp("Decompositions\\Ferrari.xlsx") %>% 
  union_all(decomp("Decompositions\\Fiat Chrysler.xlsx")) %>% 
  union_all(decomp("Decompositions\\Ford.xlsx")) %>% 
  union_all(decomp("Decompositions\\GM.xlsx")) %>% 
  union_all(decomp("Decompositions\\Honda.xlsx")) %>% 
  union_all(decomp("Decompositions\\Hyundai.xlsx")) %>% 
  union_all(decomp("Decompositions\\Nissan.xlsx")) %>% 
  union_all(decomp("Decompositions\\Tesla.xlsx")) %>% 
  union_all(decomp("Decompositions\\Toyota.xlsx")) %>% 
  union_all(decomp("Decompositions\\Volkswagen.xlsx")) %>% 
  union_all(decomp("Decompositions\\BMW.xlsx")) %>% 
  union_all(decomp("Decompositions\\Daimler.xlsx")) %>% 
  mutate(ROCE=as.numeric(ROCE),
         RNOA=as.numeric(RNOA),
         FLEV=as.numeric(FLEV),
         NBC=as.numeric(NBC),
         spread=as.numeric(spread),
         PM=as.numeric(PM),
         ATO=as.numeric(ATO),
         GPM=as.numeric(GPM),
         operating.expense.over.sales=as.numeric(operating.expense.over.sales),
         taxes_over_sales=as.numeric(taxes_over_sales),
         other_income_over_sales=as.numeric(other_income_over_sales),
         one_over_ATO=as.numeric(one_over_ATO),
         cash.over.sales=as.numeric(cash.over.sales),
         receivables.over.sales=as.numeric(receivables.over.sales),
         inventory_over_sales=as.numeric(inventory_over_sales),
         other_current_assets_over_sales=as.numeric(other_current_assets_over_sales),
         PPE_over_sales=as.numeric(PPE_over_sales),
         accounts_payable_over_sales=as.numeric(accounts_payable_over_sales),
         income_taxes_over_sales=as.numeric(income_taxes_over_sales),
         other_liabilities_over_sales=as.numeric(other_liabilities_over_sales)) %>% 
  mutate(name=case_when(str_detect(company, "BMW") ~ "BMW",
                        str_detect(company, "Daim") ~ "Daimler",
                        str_detect(company, "FORD") ~ "Ford",
                        str_detect(company, "GENERAL") ~ "GM",
                        str_detect(company, "Ferrar") ~ "Ferrari",
                        str_detect(company, "Fiat") ~ "Fiat Chrysler",
                        str_detect(company, "HONDA") ~ "Honda",
                        str_detect(company, "HYUNDAI") ~ "Hyundai",
                        str_detect(company, "NISSAN") ~ "Nissan",
                        str_detect(company, "TESLA") ~ "Tesla",
                        str_detect(company, "TOYOTA") ~ "Toyota",
                        str_detect(company, "Volkswagen") ~ "Volkswagen"),
         period=case_when(id==5 ~ 2015,
                          id==4 ~ 2016,
                          id==3 ~ 2017,
                          id==2 ~ 2018,
                          id==1 ~ 2019))

investigate01 <- function(data,
                          y,
                          title = "",
                          subtitle = "") {
  g <- ggplot(data, aes(period, y, colour = name)) +
    geom_smooth(
      aes(period, y, group = 1),
      lty = 2,
      colour = "black",
      fill = "blue",
      alpha = 0.1
    ) +
    geom_point() +
    #stat_smooth(geom = "line",lty=2,method = "lm",se=F)+
    geom_smooth(se = F) +
    theme_void() +
    labs(title = title,
         subtitle = subtitle,
         colour = "Company") +
    theme(axis.text = element_text())
  return(g)
}

```

### Investigating industry ROCE

Ferrari has a wildy changing ROCE value over the investigation period so will removed for this analysis.

```{r warning=F}

investigate01(profitability,profitability$ROCE)
```


Having removed Ferrari,  the data points look to be reasonably distributed around the average. Tesla looks to be consistently under performing within the industry as a measure of ROCE.

```{r warning=F}
profit_roce_no_outlier <- profitability %>% 
      filter(!str_detect(name,"Ferrari"))

ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$ROCE,title="Industry return on capital employed (ROCE)"))


```

### ROCE = RNOA + FLEV(Spread)
### ROCE = (PM - ATO) + FLEV(RNOA - NBC)
### ROCE = (GM/S + OE/S + T/S + OI/S) - ((1/ATO + C/S + I/S + OCA/S + PPE/S) - (pay/S + IT/S + OL/S)) + FLEV(RNOA - NBC)

# First level decomposition
### RNOA

```{r warning=F, message=F}


ggplotly(investigate01(profitability,profitability$RNOA, title="Industry return on net assets (RNOA)"))
```

### FLEV

ignoring Ferrari in FLEV

```{r warning=F, message=F}

ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$FLEV, title="Industry financial leverage (FLEV, no Ferrari)"))

```

### NBC

```{r}
ggplotly(investigate01(profitability,profitability$NBC, title="Industry net borrowing costs (NBC)"))

```

### Spread

```{r warning=F, message=F}

ggplotly(investigate01(profitability,profitability$spread, title="Industry spread (RNOA - NBC)"))


```

# Second level decomposition RNOA = PM - ATO

### PM

```{r warning=F, message=F}
ggplotly(investigate01(profitability,profitability$PM, title="Industry profit margin (OI / sales)"))
```

### ATO

```{r warning=F, message=F}
ggplotly(investigate01(profitability,profitability$ATO, title="Industry asset turnover ratio (sales / NOA)"))
```

Fiat Chrysler has an unusually high asset turnover ratio. 

# Third level decomposition (PM)

### Gross profit margin ratio (GM / Sales)

Ignoring ferrari

```{r}
ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$GPM, title="Industry gross margin ratio (GM / sales)"))

```

### Operating expense over sales

```{r}
ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$operating.expense.over.sales, title="Industry operating expense over sales ratio (OE / sales)"))
```

### Taxes over sales

```{r}
ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$taxes_over_sales, title="Industry taxes over sales ratio (taxes / sales)"))
```

### Other income over sales

```{r}
ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$other_income_over_sales, title="Industry other income over sales ratio"))
```

# Third level decomposition (ATO)

### One over ATO

```{r}
ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$one_over_ATO, title="Industry one over ATO ratio (1 / ATO)"))
```

### Cash over sales ratio

```{r}
ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$cash.over.sales, title="Industry cash over sales ratio (cash / sales)"))
```

### Receivables over sales ratio

```{r}
ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$receivables.over.sales, title="Industry receivables over sales ratio (receivables / sales)"))
```

### Inventory over sales ratio

```{r}
ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$inventory_over_sales, title="Industry inventory over sales ratio (inventory / sales)"))
```

### Other current assets over sales ratio

```{r}
ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$other_current_assets_over_sales, title="Industry other current assets over sales ratio"))
```


### PPE over sales ratio

```{r}
ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$PPE_over_sales, title="Industry PPE over sales ratio (PPE / sales)"))
```

### Payables over sales ratio

```{r}
ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$accounts_payable_over_sales, title="Industry accounts payable over sales ratio"))
```

### Income taxes over sales ratio

```{r}
ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$income_taxes_over_sales, title="Income taxes over sales ratio"))
```

### Other liabilities over sales ratio

```{r}
ggplotly(investigate01(profit_roce_no_outlier,profit_roce_no_outlier$other_liabilities_over_sales, title="Industry other liabilities over sales ratio"))
```

# First level decomposition overview
ROCE = RNOA + FLEV*spread. 

The first component (RNOA) measures the return on net operating assets. The second component (Flev*spread) measures the effects of financial leverage. ROCE is increased by adding financial leverage as long as RNOA is greater than the firm's Weighted Average Cost of Capital (WACC).


```{r}
drivers <-
    c(colnames(profitability[2]), colnames(profitability[5:23]))
  
first_level <-  profit_roce_no_outlier %>%
    filter(id==1) %>% 
    select(ROCE,RNOA,FLEV,spread,id,name) %>% 
    mutate(flev_and_spread = FLEV*spread) %>% 
    pivot_longer(cols = c(ROCE,RNOA,flev_and_spread),
                 names_to = "driver",
                 values_to = "value") %>%
    ggplot(aes(driver, value, colour = name)) +
    geom_point() +
   labs(title="First level decomposition overview (2019)")+
    coord_flip() +
    labs(colour = "Company") +
    theme_bw()
  

  ggplotly(first_level)
```




The overview shows that Tesla is not productive enough with its assets to contribute to ROCE and is essentially erroding away its assets. This shows that Tesla is making poor use of its capital assets.

# Second level decomposition overview (2019)

```{r}
second_level <-  profit_roce_no_outlier %>%
    filter(id==1) %>% 
    select(PM,ATO,id,name) %>%
    pivot_longer(cols = c(PM,ATO),
                 names_to = "driver",
                 values_to = "value") %>%
    ggplot(aes(driver, value, colour = name)) +
    geom_point() +
   labs(title="Second level decomposition overview (2019)")+
    coord_flip() +
    labs(colour = "Company") +
    theme_bw()

ggplotly(second_level) 
```

Tesla has a slightly higher than 1 ATO which suggests that they are typically using their assets more efficiently to generate revenue than other firms within the global car market, excluding Fiat Chrysler. 

A negative PM suggests that Tesla struggles to control costs effectively. The combined effect of  PM and ATO results in a negative RNOA.

# Third level decomposition overview (2019)

```{r}

third_level <-  profitability %>%
    filter(id==1) %>% 
    select(GPM,operating.expense.over.sales,taxes_over_sales,other_income_over_sales,cash.over.sales,receivables.over.sales,inventory_over_sales,other_current_assets_over_sales,PPE_over_sales,accounts_payable_over_sales,income_taxes_over_sales,other_liabilities_over_sales,id,name) %>%
    pivot_longer(cols = c(GPM,operating.expense.over.sales,taxes_over_sales,other_income_over_sales,cash.over.sales,receivables.over.sales,inventory_over_sales,other_current_assets_over_sales,PPE_over_sales,accounts_payable_over_sales,income_taxes_over_sales,other_liabilities_over_sales),
                 names_to = "driver",
                 values_to = "value") %>%
    ggplot(aes(driver, value, colour = name)) +
    geom_point() +
   labs(title="Third level decomposition overview (2019)")+
    coord_flip() +
    labs(colour = "Company") +
    theme_bw()

ggplotly(third_level) 
```

At this level, it is clear that Tesla pays a larger Tax rate as a proportion of revenue than other companies in the car industry. Tesla also has a large Property, Plant, and Equipment ratio compared to other companies. This may be because of other companies being streamlined for the production of consumer cars, whereas Tesla may be more exploratory in its business endeavours with large amounts of assets reserved for other projects. Tesla also has more capital stored in cash which is not being used to generate further value. 

# Trend analysis


```{r}
  trend_analysis <- profitability %>%
    group_by(name) %>%
    arrange(period, .by_group = TRUE) %>%
    mutate(perc_ROCE = (ROCE / lag(ROCE)) * 100)

  something <- profitability %>%
    group_by(name, period) %>%
    mutate(ROCE_change = (ROCE / lag(ROCE)))
```
  

  
  


# Common size analysis


