---
title: Recent grads
author: ~
date: '2020-07-01'
slug: recent-grads
categories: []
tags: []
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE)
```

```{r echo = FALSE, include=FALSE}
library(tidyverse)
library(plotly)
library(bbplot)
theme_set(theme_bw())
recent_grads <-
  read_csv(
    "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-10-16/recent-grads.csv"
  )

majors_processed <- recent_grads %>% 
  arrange(desc(Median)) %>% 
  mutate(Major = str_to_title(Major),
         Major = fct_reorder(Major,Median))
```
### Exploatory data analysis
```{r}
majors_processed %>%
  count(Major_category, sort = T)
```



```{r by_major_category}
recent_grads %>% 
  arrange(desc(Median)) %>% 
  view()
by_major_category <- majors_processed %>% 
  filter(!is.na(Total)) %>% 
  group_by(Major_category) %>% 
  summarize(Men = sum(Men),
    Women = sum(Women),
    Total = sum(Total),
    MedianSalary = sum(Median*Sample_size)/sum(Sample_size)) %>% 
  mutate(ShareWomen = Women / Total) %>% 
  arrange(desc(ShareWomen))
```

```{r}
majors_processed %>%
  ggplot(aes(Median)) +
  geom_histogram()
```

### Metallurgical gender mix

```{r}
library(ggrepel)
majors_processed %>%
  mutate(Major_category=fct_reorder(Major_category,ShareWomen)) %>% 
  ggplot(aes(fct_lump(Major_category, 20), ShareWomen, fill =
               Major_category),
         label=ShareWomen) +
  geom_boxplot(show.legend = F) +
  coord_flip() +
  ggtitle("Metallurgical mix")+
  theme_bw() +
  geom_hline(yintercept = 0.153, lty = 2)+
  annotate("text",label="15.3% female",x=9,y=0.1,angle=90)+
  xlab("")
```


### Comparing income distributions across major category

```{r}
majors_processed %>% # BOXPLOT COMPARING EARNINGS ACROSS MAJOR CATEGORY
  mutate(Major_category = fct_reorder(Major_category, Median)) %>%
  ggplot(aes(Major_category, Median,fill=Major_category)) +
  geom_boxplot(show.legend = F) +
  coord_flip() +
  xlab("")+
  scale_y_log10(labels = scales::dollar_format())
```


### Median earnings across major categories

```{r}
majors_processed %>% 
  group_by(Major_category) %>% 
  summarise(Median=median(Median)) %>% 
  mutate(Major_category = fct_reorder(Major_category, Median)) %>%
  ggplot(aes(Major_category,Median,fill=Major_category))+
  geom_col(show.legend = FALSE)+
  coord_flip()
```

### What are the highest earning majors?

```{r warning=FALSE}
majors_processed %>% # INTERQUARTILE RANGE OF HIGHEST EARNING MAJORS
  arrange(desc(Median)) %>% 
  select(Major,Major_category,Median,P25th,P75th) %>% 
  head(20) %>% 
  mutate(Major=fct_reorder(Major,Median)) %>% 
  ggplot(aes(Major,Median,colour=Major_category))+
  geom_point()+
  coord_flip()+
  geom_errorbar(aes(ymin=P25th,ymax=P75th))+
  expand_limits(y=0)
```



### Business subjects - Highest earning majors
```{r}
majors_processed %>% 
  filter(Major_category=='Business') %>% 
  mutate(Major=fct_reorder(Major,Median)) %>% 
  ggplot(aes(Major,Median,fill=Major)) +
  geom_col(show.legend=FALSE)+
  xlab("")+
  coord_flip()+
  ggtitle("Highest earning majors in business")
```


### Male dominated majors

```{r}

library(ggrepel)
majors_processed %>% 
  arrange(ShareWomen) %>% 
  head(20) %>% 
  mutate(Major=fct_reorder(Major,ShareWomen)) %>% 
  ggplot(aes(Major,ShareWomen))+
  geom_point()+
  coord_flip()
```

### Mapping share of women and median earnings per major

```{r}
majors_processed %>% 
  filter(Sample_size>30) %>% 
  ggplot(aes(desc(ShareWomen),Median))+
  geom_point()+
  scale_y_log10(labels=scales::dollar_format())+
  geom_smooth(method='lm')+
  geom_text_repel(aes(label=Sample_size,alpha=0.2))+
  theme_bw()

summary(lm(Median~ShareWomen,recent_grads))

```

### Percentage share of women in the 20 most popular majors

```{r}
majors_processed %>% 
  arrange(desc(Total)) %>% 
  mutate(Major=fct_reorder(Major,Total)) %>% 
  head(20) %>% 
  ggplot(aes(Major,Total,fill=ShareWomen))+
  geom_col()+
  scale_y_continuous(label=scales::comma_format())+
  coord_flip() 
```

### What are the most common Major Categories?

```{r}
majors_processed %>% 
  count(Major_category, wt= Total, sort=TRUE) %>% 
  mutate(Major_category = fct_reorder(Major_category, n)) %>% 
  ggplot(aes(Major_category, n, fill = Major_category))+
  geom_col()+
  coord_flip()+
  labs(title="Most common major categories",
    x="",
    y="Total number of graduates"
  )+
  scale_y_continuous(label = scales::comma_format())+
  theme_bw()+
  theme(legend.position="none")
```


### What were the most common Majors?

```{r}
majors_processed %>% 
  mutate(Major=fct_reorder(Major,Total)) %>% 
  arrange(desc(Total)) %>% 
  head(20) %>% 
  ggplot(aes(Major,Total,fill=Major))+
  geom_col()+
  theme(legend.position = "none")+
  scale_y_continuous(label=scales::comma_format())+
  coord_flip()
  
```

### How does gener mix relate to typical earnings?

```{r}
majors_processed %>% 
  arrange(desc(Total)) %>% 
  head(20) %>% 
  mutate(Major=fct_reorder(Major, Total)) %>% 
  gather(Gender, Number, Men, Women) %>% 
  ggplot(aes(Major, Number, fill = Gender))+
  geom_col()+
  scale_y_continuous(label=scales::comma_format())+
  coord_flip()
```



```{r}

by_major_category %>% 
  ggplot(aes(ShareWomen,MedianSalary))+
  geom_point()+
  geom_smooth(method="lm")+
  geom_text_repel(aes(label=Major_category),force=0.2)+expand_limits(y=0)+
  labs(title="Relationship between median salary and proportion of women",
       subtitle="Ordered by major category")
  
```
```{r}
library(plotly)
g <- majors_processed %>% 
  mutate(Major_category=fct_lump(Major_category,7)) %>% 
  ggplot(aes(ShareWomen,Median, colour= Major_category,size=Sample_size))+
  geom_point(aes(label=Major))+
  geom_smooth(aes(group=1),method="lm")+
  expand_limits(y=0)+
  labs(title="Relationship between median salary and proportion of women",
       subtitle = "Ordered by major and coloured by major category",
       x="Percentage share of women in the field",
       y="Median salary income")+
  theme(legend.position = 'none')+
  annotate("text",x=0.8,y=max(majors_processed$Median)-2000,hjust=1,vjust=1,label="Size refers to sample size")+
  annotate("text",x=0.8,y=max(majors_processed$Median)-8000,hjust=1,vjust=1,label="Colour refers to major category")+
  scale_y_continuous(labels=scales::dollar_format())+
  scale_x_continuous(labels=scales::percent_format())

   
ggplotly(g)
```
 
```{r}
majors_processed %>% 
  select(Major, Total, ShareWomen, Sample_size, Median) %>% 
  lm(Median ~ ShareWomen, data = ., weights = Sample_size) %>% 
  summary()
```