---
title: Energy sector
author: ~
date: '2020-10-01'
slug: energyhhi
categories: []
tags: []
---

```{r setup, include=FALSE, message=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE)
```



# UK energy market competitiveness

### Herfindahl-Hirschman Index

Regulators use the HHI Index using the 50 largest companies in a particular industry to determine if that industry should be considered competitive or as close to being a monopoly.

A market with an HHI of less than 1,500 is considered to be a competitive marketplace, an HHI of 1,500 to 2,500 to be a moderately concentrated marketplace, and an HHI of 2,500 or greater to be a highly concentrated marketplace.



$$HHI = 10,000 [s^2_1+s^2_2+s^2_3+...+s^2_n]$$


```{r}
library(tidyverse)
```

```{r}
data <- readxl::read_excel(file.path("data", "energymarket.xlsx")) %>%
  filter(!is.na(share)) %>%
  mutate(no_customers = as.numeric(no_customers))

data_HHI <- data %>%
  mutate(prop = (no_customers / sum(no_customers)) ^ 2) %>%
  mutate(HHI = 10000 * sum(prop))

HHI <- mean(data_HHI$HHI)

```

The UK energy market has a HHI of <a><span style="color: red;">`r round(HHI,2)`</span></a> showing a relatively competitive marketplace. 



# UK energy market biggest suppliers

```{r}
data %>% 
  mutate(name = fct_reorder(name, no_customers),
         row = row_number()) %>% 
  arrange(desc(no_customers)) %>% 
  ggplot(aes(name, no_customers))+
    geom_segment(aes(xend = name, yend = 0), size = 1.5) +
    geom_point(shape = 21, colour = "black", aes(fill = "blue"), size = 12) +
    geom_text(size = 3, aes(label = paste(round(no_customers / 1000000, 1), "m", sep = "")))+
  scale_color_manual(values = c("orange","dodgerblue"), aesthetics = c("fill"))+
  scale_color_manual(values = c("orange","black"), aesthetics = c("colour"))+
  scale_y_continuous(labels = scales::comma_format())+
  labs(title = "No. Customers of UK Energy Suppliers",
       x = "",
       y = "No. Customers")+
  theme_void()+
  theme(legend.position = "none",axis.text.y = element_text(hjust = 0.95))+
  coord_flip()

```



